Reproducible Summary Tables with the gtsummary Package

### 2020-12-11 RJtemplate_gtsummary_submission.tex

To show use of gtsummary functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B as well as the outcome of tumor response to the treatment.
Each variable in the data frame has been assigned an attribute label (i.e. \texttt{attr(trial\$trt, "label") == "Chemotherapy Treatment"}) with the labelled[add ref] package. 
These labels are displayed in the {gtsummary} tables by default. Using {gtsummary} on a data frame without labels will print variable names in place of variable labels with the option to update the text displayed.

@@

The default styling (e.g. statistics displayed in \texttt{tbl\_summary()}, how p-values are rounded, decimal separator, and more) follow the reporting guidelines from European Urology, The Journal of Urology, Urology, and the British Journal of Urology International.[]

>>>>

To show use of gtsummary functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B as well as the outcome of tumor response to the treatment.
Each variable in the data frame has been assigned an attribute label (i.e. \texttt{attr(trial\$trt, "label") == "Chemotherapy Treatment"}) with the labelled package\citep{labelled}. 
These labels are displayed in the {gtsummary} tables by default. Using {gtsummary} on a data frame without labels will print variable names in place of variable labels with the option to update the text displayed.

@@

The default styling (e.g. statistics displayed in \texttt{tbl\_summary()}, how p-values are rounded, decimal separator, and more) follow the reporting guidelines from European Urology, The Journal of Urology, Urology, and the British Journal of Urology International\citep{assel2019guidelines}.
